Are environmental and geographic effective surrogates for genetic variation in conservation planning?

### 2016-01-17 article/supporting_information.Rmd
- update genetic mds to use varying number of k-values till stress is suitable

```{r, echo=FALSE}
plot.spp.mds <- function(i) {
	# define function
	make.mds.plot <- function(j,k) {
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey20', color='grey80') +
			geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
				group='group', fill=paste0(unique(spp.samples.DF$species)[i], '_', j, '_d',k)),
				alpha=0.8, color='grey10') +
			guides(fill=guide_legend(title=' ')) +
			theme_classic() +
			theme(axis.ticks=element_blank(), axis.text=element_blank(),
				plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank()) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0.05),
				ylim=buffered.range(grid.FPLY$lat, 0.05)
			) +
			xlab('') +
			ylab('') +
			ggtitle(paste0(j,' (',k,')'))
	}
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	plotLST <- list()
	# make adaptive plot
	if (adapt.col %in% names(grid.FPLY)) {
		for (k in seq_len(mds.params.LST[[MODE]]$k))
			plotLST <- append(plotLST, list(make.mds.plot('adaptive', k)))
	} 
	# make neutral plot
	if (neutral.col %in% names(grid.FPLY)) {
		for (k in seq_len(mds.params.LST[[MODE]]$k))
			plotLST <- append(plotLST, list(make.mds.plot('neutral', k)))
	} 
	# make plot
	do.call(
		grid.arrange,
		append(
			plotLST,
			list(ncol=6)
		)
	)
}
```

@@

```{r, echo=FALSE}
knitr::kable(
	format.table(
		filter(
			ldply(
				seq_along(unique(spp.samples.DF$species)), 
				function(i) {
					ldply(
						seq_along(spp.mds.LST[[i]]),
						function(j) {
						data.frame(
							Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
							Loci=names(spp.mds.LST[[i]])[j],
							Stress=ifelse(is.null(spp.mds.LST[[i]][[j]]), NA_real_, spp.mds.LST[[i]][[j]]$stress),
							Converged=ifelse(is.null(spp.mds.LST[[i]][[j]]), NA_real_, spp.mds.LST[[i]][[j]]$converged)
						)
					})
				}
			),
			!is.na(Stress)
		),
		omit=c('Loci','Converged')
	),
	digits=2,
	caption='Summary of non-metric multi-dimensional scaling (MDS) analyses on genetic variation for each species.',
	col.names=c('Species', 'Loci Type', 'NMDS Stress', 'Converged'),
	align=c('l', 'c', 'c', 'c')
)
```

>>>>

```{r, echo=FALSE}
plot.spp.mds <- function(i) {
	# define function
	make.mds.plot <- function(j,k) {
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey20', color='grey80') +
			geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
				group='group', fill=paste0(unique(spp.samples.DF$species)[i], '_', j, '_d',k)),
				alpha=0.8, color='grey10') +
			guides(fill=guide_legend(title=' ')) +
			theme_classic() +
			theme(axis.ticks=element_blank(), axis.text=element_blank(),
				plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank()) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0.05),
				ylim=buffered.range(grid.FPLY$lat, 0.05)
			) +
			xlab('') +
			ylab('') +
			ggtitle(paste0(j,' (',k,')'))
	}
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	plotLST <- list()
	# make adaptive plot
	if (adapt.col %in% names(grid.FPLY)) {
		for (k in seq_len(spp.mds.LST[[i]][['adaptive']]$ndim))
			plotLST <- append(plotLST, list(make.mds.plot('adaptive', k)))
	} 
	# make neutral plot
	if (neutral.col %in% names(grid.FPLY)) {
		for (k in seq_len(spp.mds.LST[[i]][['neutral']]$ndim))
			plotLST <- append(plotLST, list(make.mds.plot('neutral', k)))
	}
	# make plot
	do.call(
		grid.arrange,
		append(
			plotLST,
			list(ncol=6)
		)
	)
}
```

@@

```{r, echo=FALSE}
knitr::kable(
	format.table(
		filter(
			ldply(
				seq_along(unique(spp.samples.DF$species)), 
				function(i) {
					ldply(
						seq_along(spp.mds.LST[[i]]),
						function(j) {
						data.frame(
							Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
							Loci=names(spp.mds.LST[[i]])[j],
							k=ifelse(is.null(spp.mds.LST[[i]][[j]]), NA_integer_, spp.mds.LST[[i]][[j]]$ndim),
							Stress=ifelse(is.null(spp.mds.LST[[i]][[j]]), NA_real_, spp.mds.LST[[i]][[j]]$stress),
							Converged=ifelse(is.null(spp.mds.LST[[i]][[j]]), NA, spp.mds.LST[[i]][[j]]$converged)
						)
					})
				}
			),
			!is.na(Stress)
		),
		omit=c('Loci','Converged')
	),
	digits=2,
	caption='Summary of non-metric multi-dimensional scaling (MDS) analyses on genetic variation for each species.',
	col.names=c('Species', 'Loci Type', 'k', 'NMDS Stress', 'Converged'),
	align=c('l', 'c', 'c', 'c', 'c')
)
```
